\documentclass{article}

\usepackage{fancyhdr}
\usepackage{mathtools}

\pagestyle{fancy}

\lhead{Robin Touche 900610-3270}
\rhead{robint@student.chalmers.se}

\begin{document}
\section*{Home problem 2}

\setcounter{section}{2}
\subsection{}
\subsubsection*{a}

The total number of permutations is $N!$. To remove shifted version we have to
divide this number by $N$ since each cycle can start at any of the $N$ cities.
Then we need to further divide by $2$ to remove mirrored paths as well.

The final answer is thus $\frac{N!}{2N}$.

\subsubsection*{b,c,d}

Note that to be able to run any of the srcipts, the folder TSPgraphics needs to
be added to the path. Also, \emph{b} and \emph{d} have many conflicting names
so make sure to not load them at the same time.

Also of note is that I pre-calculate the distances between all cities and pass
that matrix around (in the function arguments in \emph{b,d} and by a global
matrix, unfortunately, in \emph{d}) to avoid having to re-calculate them every
step of the way.  This gave a speedup of up to 10x on some of the systems I
tested. (I asked Mattias about this and he gave me permission to use it.)

The shortest path length for each algorithm can be seen in the table below. The
parameters used in these cases have been left in the code file.

\begin{center}
  \begin{tabular}{| c | c |}
    \hline
    GA & 178.5903 \\
    \hline
    GA(NN) & 132.2687 \\
    \hline
    ACO & 121.10525 \\
    \hline
  \end{tabular}
\end{center}

The ACO code does not terminate until it finds a solution $< 123$ length units
so just the value is not really telling the whole story. The algorithm usually
terminates at around $300$ iterations but I have had runs everuwhere from 17 to
$1100$ iterations so it can vary. The value in the table took $353$ iterations.

\subsection{}

Both problems share most of the code. The only differences is in the main files
(PSO22x) and the evaluation.

\subsubsection*{a}

The minimum found by the algorithm is $f(5,4) = 1$. This algorithm is fairly
fast so $10000$ iterations does not take much time. It starts to converge
towards accurate results with as few as $300$ iterations.

\subsubsection*{b}

The two minimums found are:
\begin{align*}
  f(0, 12, 23, 17, 6) &= -737 \\
  f(0, 11, 22, 16, 6) &= -737
\end{align*}

This function is not as lenient with the number of iterations as \emph{2.2a} but
$10000$ tends to find one of the minimums every time.

\subsection{}
Not implemented.

\subsection{}


\end{document}
